Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2015-11-30 manuscript/manuscript.Rnw
fix up the sequencing and the human length error

\DLA{Fix how the sequencing was done}

All RNA-Seq mRNA isolation, library construction, and Illumina
sequencing was performed by the Applied Genomics Technology Center
(AGTC) at Wayne State University School of Medicine using 2.5-5 µg of
total RNA and standard Illumina protocol. Paired-end sequencing was
performed using the Illumina Genome Analyzer II with an insert size of
230 base pairs (bp). \textit{Bos}, \textit{Loxodonta}, and
\textit{Monodelphis} were sequenced with read lengths of 75 bp;
\textit{Canis}, \textit{Homo}, and \textit{Pan} were sequenced with
read lengths of 150 bp.

For comparison, additional sequences of placenta in \textit{Mus
  musculus} \cite{Wang.ea2011:surveyfornovelimprinted} and
\textit{Homo sapiens}
\cite{Hughes.ea2015:Evaluatingintra-andinter-individual} were obtained
from the \ac{SRA}.

@@

All 1:1 orthologues present among \textit{D. novemcinctus}, \textit{P.
  troglodytes}, \textit{B. taurus}, \textit{C. familiaris}, \textit{L.
  africana}, \textit{M. musculus}, \textit{H. sapiens}, and \textit{M.
  domestica} were determined using Ensembl v.80 gene trees via
Biomart\cite{Kasprzyk2011:BioMartdrivingparadigmchange} using the
biomaRt R package \DLA{Cite the biomaRt package}. A total of
\Sexpr{combined.fpkm[species!="homo sapiens" & mean_fpkm >=
  1,length(unique(human_short_name))]} 1:1 orthologous genes were
expressed in at least one species. Of these,
\Sexpr{combined.fpkm[species!="homo sapiens" & mean_fpkm >=
  10,length(unique(human_short_name))]} 1:1 orthologous genes with
\ac{FPKM} $\ge 10$ were retained for future analyses of gene
expression evolution described below.

>>>>

All RNA-Seq mRNA isolation, library construction, and Illumina
sequencing was performed by the Applied Genomics Technology Center
(AGTC) at Wayne State University School of Medicine using 2.5-5 µg of
total RNA and standard Illumina protocol. Paired-end sequencing was
performed using the Illumina Genome Analyzer II with an insert size of
230 base pairs (bp). Read lengths for species are shown in
\cref{tab:ref_genome_aligned_species}.

\subsubsection{Additional Sequences}

For more complete comparisons additional sequences of placenta in
\textit{Mus musculus} \cite{Wang.ea2011:surveyfornovelimprinted},
\textit{Homo sapiens}
\cite{Hughes.ea2015:Evaluatingintra-andinter-individual} \textit{Equus
  caballus} \DLA{citation}, \textit{Ovis aries} \DLA{citation}, and
\textit{Sus scrofa} \DLA{citation} were obtained from the \ac{SRA}
(Supplemental \cref{tab:srr_numbers}).

@@

All 1:1 orthologues present among \textit{D. novemcinctus}, \textit{P.
  troglodytes}, \textit{B. taurus}, \textit{C. familiaris}, \textit{L.
  africana}, \textit{M. musculus}, \textit{H. sapiens}, and \textit{M.
  domestica} were determined using Ensembl v.80 gene trees via
Biomart\cite{Kasprzyk2011:BioMartdrivingparadigmchange} using the
biomaRt R package \DLA{Cite the biomaRt package}. A total of
\Sexpr{combined.fpkm[species!="homo sapiens" & mean_fpkm >=
  1,length(unique(human_name))]} 1:1 orthologous genes were
expressed in at least one species. Of these,
\Sexpr{combined.fpkm[species!="homo sapiens" & mean_fpkm >=
  10,length(unique(human_name))]} 1:1 orthologous genes with
\ac{FPKM} $\ge 10$ were retained for future analyses of gene
expression evolution described below.

### 2015-11-30 manuscript/supplemental_material.Rnw
fix up the sequencing and the human length error

>>>>

\section{Sequence Read Archive}

\DLA{Add in SRR and GSE numbers for everything here once I have them.}

\begin{table}
  \begin{tabular}{c c p{3in}}
    \toprule
    Species                       & Experiment Number & Sample Number(s) \\
    \midrule
    \textit{Ateles fusciceps}     &  & \\
    \textit{Bos taurus}           &  & \\
    \textit{Canis familiaris}     &  & \\
    \textit{Dasypus novemcinctus} &  & \\
    \textit{Equus caballus}       &  & SRR850299,  SRR850300 \\
    \textit{Loxodonta africana}   &  & \\
    \textit{Homo sapiens}         & GSE66622 & SRR1850945,
                                               SRR1850946, 
                                               SRR1850951, 
                                               SRR1850952, 
                                               SRR1850953, 
                                               SRR1850954, 
                                               SRR1850957, 
                                               SRR1850958, 
                                               SRR1850965, 
                                               SRR1850966, 
                                               SRR1850975, 
                                               SRR1850976, 
                                               SRR1850983, 
                                               SRR1850984, 
                                               SRR1850987, 
                                               SRR1850988, 
                                               SRR1850991, 
                                               SRR1850992, 
                                               SRR1850993, 
                                               SRR1850994, 
                                               SRR1850995, 
                                               SRR1850996, 
                                               SRR1851003, 
                                               SRR1851004, 
                                               SRR1851011, 
                                               SRR1851012 \\
    \textit{Monodelphis domestica} & & \\
    \textit{Mus musculus}         &  & SRR243594,
                                       SRR243595,
                                       SRR243596,
                                       SRR243597,
                                       SRR243598,
                                       SRR243599,
                                       SRR243600,
                                       SRR243601,
                                       SRR243602,
                                       SRR243586,
                                       SRR243587,
                                       SRR243588,
                                       SRR243589,
                                       SRR243590,
                                       SRR243591,
                                       SRR243592,
                                       SRR243593\\
    \textit{Nannospalax galili}   &  & \\
    \textit{Ovis aries}           &  & ERR489144, ERR489145\\
    \textit{Pan paniscus}         &  & \\
    \textit{Spalax carmeli}       &  & \\
    \textit{Sus scrofa}           &           & SRR543893 \\
    \bottomrule
  \end{tabular}
  \caption{Species, experiment and species numbers used in the analyses presented in this paper}
  \label{tab:srr_numbers}
\end{table}

\begin{table}
  \begin{tabular}
  \end{tabular}
\end{table}
